Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-22 Scripts/Initial_Analysis.Rmd
Finished analysis for sensitivity of historical s.d.

sens_paths <- list.files("~/Desktop/Sens_analysis/Emergence_alt_sens",full.names = T)

# Load all sp in one table
Eme_Alt_Res <- bind_rows(lapply(sens_paths, fread)) %>% 
  mutate(method= "alt") %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(Matching_names,
            by=  "sf_eez_name") %>% 
  clean_names() %>% 
  mutate(tresh = str_to_lower(tresh)) %>% 
  filter(emerging_yr != 2100)

@@

## General numbers

@@

# Looks like there is no difference in the total number of emerging stocks
# method emerging_stocks prop_total
# alt                158       85.9
# org                147       79.9

@@

# Looks like the alternative method sets a later mean ToE but no real difference in s.d. min nor max
# method  mean    sd   min   max
# alt    2054.  29.2  2007  2099
# org    2029.  25.4  2006  2098

@@

@@

>>>>

fread2 <- function(x){

  tb <- fread(x)

  if(nrow(tb) >0){
    return(tb)
  }

sens_paths <- list.files(my_path("R","Emergence_alt_sens"),full.names = T)

# Load all sp in one table
Eme_Alt_Res <- bind_rows(lapply(sens_paths, fread2)) %>% 
  mutate(method= "alt") %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(Matching_names,
            by=  "sf_eez_name") %>% 
  clean_names() %>% 
  mutate(tresh = str_to_lower(tresh)) %>% 
  filter(emerging_yr != 2100)

@@

#### General numbers

@@

# Looks like there is no difference in the total number of emerging stocks
 # tresh     method emerging_stocks prop_total
# 1 tresh_one alt               6665      116. 
# 2 tresh_one org               5729      100  
# 3 tresh_two alt               5258       91.8
# 4 tresh_two org               4108       71.7

@@

# Looks like the alternative method sets a later mean ToE but no real difference in s.d. min nor max
#  tresh     method  mean    sd   min   max
# 1 tresh_one alt    2055.  28.7  2007  2099
# 2 tresh_one org    2029.  26.7  2006  2099
# 3 tresh_two alt    2057.  28.6  2007  2099
# 4 tresh_two org    2036.  28.1  2006  2099

@@

#### Area plots 
```{r read_raw_data, eval = T, echo = F}

@@

  # Save plot
  save_plot(
    "./Figures/cumu_per_freq_sens.png",
    plot_all,
    base_height = 5,
    base_width = 12
  )

#### Comparative map

```{r}

# Per EEZs
Eez_d_hist <- sens_data %>% 
  group_by(eezid,sau_fishing_entity,tresh,method) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

# Estimate the value (catch and USD) of emerging species
Eme_value_data <- sens_data %>% 
  group_by(sau_fishing_entity,fishing_entity_id,tresh,taxon_key,method) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,tresh,variable,method) %>% 
  summarise(
   sum_value = sum(value,na.rm=T),
    n_taxa = length(unique(taxon_key)) 
  )

fish_d_hist <- sens_data %>% 
  group_by(sau_fishing_entity,tresh,method) %>% 
  summarise(
    value = length(unique(taxon_key))
    ) %>% 
  filter(!is.na(sau_fishing_entity))

# -------------------------- #
# Call plot
# -------------------------- #
tresh_list <- "tresh_two"

  name_save <- paste("./Figures/emer_map_sens_",tresh_list,".png",sep = "")

  # Value Map
  World_map_part <- World_map_nemer %>% 
  filter(
    tresh ==  tresh_list,
    variable == "value"
  )

  # ToE Map 
  toe_map_data <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list,
           metric == "mean_yr")

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_part,
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c(">2100",seq(2075,2000,-25)) # not inluding the > because we
    ) +
    my_ggtheme_m() +
    facet_wrap(~method,
               nrow = 2)

  ggsave(name_save,
         width = 10,
         height = 6,
         units = "in"
  )
